Tables for PM2.5 Paper Manuscript

### 2021-05-31 code/data-viz/manuscript-tables.Rmd
update plot lables and shapes

# Figure 1a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Biomass", 8, 9) %>% 
    group_rows("Coal", 10, 11) %>%
    group_rows("Salt", 12, 13) %>% 
    group_rows("Oil", 14, 15) %>% 
    group_rows("Steel", 16, 17) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

@@

# Figure 1b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure 2a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Coal", 8, 9) %>%
    group_rows("Oil", 10, 11) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure 2b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure x
```{r}
table_fk <- function(data, cmp, cuz, em){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(!Index %in% c("Na", "Cl")) %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 3, 6) %>%   # same result with group 1=
    group_rows("Metals", 7, 10) %>% 
    group_rows("Traffic", 11, 14) %>% 
    group_rows("Coal", 15, 18) %>% 
    group_rows("Oil", 19, 22) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

@@

# Figure x2
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

>>>>

# Figure 1a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Biomass", 8, 9) %>% 
    group_rows("Coal", 10, 11) %>%
    group_rows("Salt", 12, 13) %>% 
    group_rows("Oil", 14, 15) %>% 
    group_rows("Steel", 16, 17) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

@@

# Figure 1b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure 2a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Coal", 8, 9) %>%
    group_rows("Oil", 10, 11) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure 2b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

@@

# Figure x
```{r}
table_fk <- function(data, cmp, cuz, em){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(!Index %in% c("Na", "Cl")) %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 3, 6) %>%   # same result with group 1=
    group_rows("Metals", 7, 10) %>% 
    group_rows("Traffic", 11, 14) %>% 
    group_rows("Coal", 15, 18) %>% 
    group_rows("Oil", 19, 22) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

@@

# Figure x2
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    group_rows("Soil", 3, 6) %>%   # same result with group 1=
    group_rows("Metals", 7, 10) %>% 
    group_rows("Traffic", 11, 14) %>% 
    group_rows("Coal", 15, 18) %>% 
    group_rows("Oil", 19, 22) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}
